Total Score

### 2023-02-04 src/MSAtotal_scores.Rmd
working on bar chart

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$inverted_n_eal_score[i]
                  )
  criteria_all$stud_EAL_total[i] = weighted.mean(cbsa_data, criteria_weights_students)
}

@@

@@

### Using climate weight 50 and proportional others with EAL
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$inverted_n_eal_score[i]
                  )
  criteria_all$score_climate50_prop_EAL[i] = weighted.mean(cbsa_data, weights_climate50_prop) 
}

@@

sheet_write(criteria_all, ss = "https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=0", sheet = "FINAL_total_score")
```

```{r data viz, eval = FALSE}

score_tidy <- criteria_all %>% 
  pivot_longer(cols = c(4:18),
               names_to = "criteria",
               values_to = "criteria_score") %>% 
  filter(city_msa != "Portland") %>% 
  group_by(city_msa) %>% 
  filter(criteria %in% c("real_estate_score", "landlord_score", "financial_score", "climate_impact", "electricity", "climate_risk", "climate_EAL_risk", "health_impact", "electricity"))

ggplot(data = score_tidy, aes(y = city_msa, x = criteria_score, fill = criteria)) + 
    geom_col()

>>>>

@@

```{r student weights with EAL, eval = FALSE}
size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$inverted_n_eal_score[i]
                  )
  criteria_all$stud_EAL_total[i] = weighted.mean(cbsa_data, criteria_weights_students)
}
```

@@

```{r Climate with 50 & proportional others with EAL, eval=FALSE}
### Using climate weight 50 and proportional others with EAL
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$inverted_n_eal_score[i]
                  )
  criteria_all$score_climate50_prop_EAL[i] = weighted.mean(cbsa_data, weights_climate50_prop) 
}

@@

#sheet_write(criteria_all, ss = "https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=0", sheet = "FINAL_total_score")
```

```{r data viz}
## read in weighted criteria sheet
weighted_criteria <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=0", sheet = "wtd_criteria_Owen")

score_tidy <- weighted_criteria %>% 
  pivot_longer(cols = c(4:9), # selecting criteria cols
               names_to = "criteria",
               values_to = "criteria_score") %>% 
 filter(city_msa != "Portland") # removing portland (negative number)

ggplot(data = score_tidy, aes(y = reorder(cbsa, FINAL_owen_SCORE), x = criteria_score, fill = criteria_labels)) + 
    geom_col(aes(fill = criteria)) +
  labs(x = "Total Score (Client)",
       y = " ") +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
scale_fill_discrete(labels=c('Climate Risk', 'CO2 Emissions', 'Electricity', "Finances", "Real Estate", "Landlord")) +
   scale_fill_manual(values = c("#FDB462", "gold", "palevioletred1",  "#BC80BD", "#6699CC", "#44AA99"))
